\section{Assets}
Smoking Games' assets can be categorized into tangible and intangible assets. Every service consulted or used by Smoking Games which benefits them or is more or less essential for business processes is considered an asset.
\subsection{Tangible Assets}
Besides the obvious assets like building, computers or other hardware, power, water and data and telecommunication services are essential for Smoking Games' business processes and procedures and are therefore considered an asset because when one of these services is not available anymore it will inflict damage on their business economy. All tangible assets are shown in table \ref{tab:TangibleAssets}.
\begin{table}[h]
	\centering
	\begin{tabular}{l | l}
		\textbf{Asset} & \textbf{Economic Benefit}\\\hline\hline
		\parbox[t]{6cm}{Office Building and Offices} & \parbox[t]{6cm}{Provides space for employees}\\\hline
		\parbox[t]{6cm}{Office Equipment} & \parbox[t]{6cm}{Provides the necessary equipment for employees}\\\hline
		\parbox[t]{6cm}{in-house IT-system \& File Storage} & \parbox[t]{6cm}{Provides maintainability and storage of customer information and applications}\\\hline
		\parbox[t]{6cm}{Server Farm} & \parbox[t]{6cm}{Provides accessibility for customers and employees}\\\hline
		\parbox[t]{6cm}{Other Machines} & \parbox[t]{6cm}{Used for the production of goods}\\\hline
		\parbox[t]{6cm}{Other Hardware} & \parbox[t]{6cm}{Used for different business processes}\\\hline
		\parbox[t]{6cm}{Access Control} & \parbox[t]{6cm}{Provides selective restriction of access to resources}\\\hline
		\parbox[t]{6cm}{External Security Services (e.g. security guard, alarm system, CCTV cameras)} & \parbox[t]{6cm}{Provides protection of other assets or people}\\\hline
		\parbox[t]{6cm}{Emergency Generator} & \parbox[t]{6cm}{Provides backup power}\\\hline
		\parbox[t]{6cm}{Data and Telecommunication, Power \& Water Services} & \parbox[t]{6cm}{Provides essential accessibility for business processes}\\\hline
		\parbox[t]{6cm}{Renovation} & \parbox[t]{6cm}{Provides maintainability of e.g. buildings}\\
	\end{tabular}
	\caption{Tangible Assets}\label{tab:TangibleAssets}
\end{table}
\subsection{Intangible Assets}
Smoking Games has been in the video game development business for six years and they have (as mentioned earlier) become well-known for its critically acclaimed games which helped them establish a business reputation in the public domain as well as their name is being recognized by people more and more often. Both have increased even more after they launched their distribution platform.\\
With the development of new software Smoking Games acquired new patents, logos, formulas and of course copyrights.\\
For additional assets see table \ref{tab:OtherTangibleAssets}. 
\begin{table}[h]
	\centering
	\begin{tabular}{l | l}
		\textbf{Asset Category} & \textbf{Asset}\\\hline\hline
		Information & \parbox[t]{7cm}{database information, employee contracts, consulting contracts, documentation,
manuals, procedures, incident response plans, business continuity plans, client data and
information, personal information, employee records, finance records, software licenses
and other}\\\hline
		Employees & \parbox[t]{7cm}{experience, information and knowledge}
	\end{tabular}
	\caption{Other Intengible Assets}\label{tab:OtherTangibleAssets}
\end{table}
\subsection{Asset Classification}
Smoking Games' assets can be classified as one of the following, with respect to their security needs.\\
\medskip
\begin{itemize}
	\item \textbf{Public:} Information and assets which is/are legally distributed/available and otherwise non-threatening to the company or its customers. This is for example information distributed through Smoking Games' website and information used in PR-campaigns.
	\item \textbf{Internal:} This is information and assets which is/are not a critical threat to the business, but is not meant to be available for the public. Disclosure of this information will yield minimal impact on the company’s daily operations, but will result in a breach of trust either with the public or customers. This involves work schedules, superficial business information and other.
	\item \textbf{Confidential:} Information and assets which is/are sensitive, business critical or otherwise legally obliged to be held confidential. Disclosure of this information will have an impact to the company in a way which disrupts or or threatens the company’s daily operations. This involves, among else, information related to the privacy act, business procedures, and client information.
\end{itemize}