\newpage
\section{Network and Security}
To provide their customers security regarding their information, Smoking Games maintain their own in-house IT-system and file storage. This also gives the employees easy access to customer information with respect to the C.I.A. principles (confidentiality, integrity, availability).
\subsection{Network}
Smoking Games host their own Web services inside the building. Maintenance of these services and the rest of the network is the responsibility of Smoking Games' own IT department.\\
The company network is divided in, roughly speaking, two parts: the internal network and the perimeter network. The perimeter network is connected to an external router, which in turn is connected to the external network (WAN or internet), Web services and an internal router. The Web services include access to the website, a VPN access for consulting purposes, and other. A backbone is placed between the internal router and the internal network (which itself is consisting of two parts). The file storage and database servers are part of the internal network. An overview of the network topology is shown in figure foo.\\
To detect suspicious traffic, an IDS (intrusion detection system) is installed in the perimeter network right before the internal router and integrated in the backbone. That way all the traffic to and in the sensitive area is being logged.\\
The rest of the internal network consists of work machines, a database server and a file server which is used as a subversion repository, when the consultants work together on a project.\\
The database server contains a lot of information about customers. This is highly sensitive information and access is only given to authorized personnel.\\
A wireless network is also being provided, but it is not connected to the other network.
\subsection{Rules and Regulation}
As BYOD (bring your own device) is becoming more and more a security risk for companies, Smoking Games have strict policies for personal mobile devices. They are only allowed to use in the wireless area and (of course) outside the company network. Also, no information regarding the customers or business projects is allowed to keep or use on the devices. An exception are personal flash drives: they are allowed to use in both networks, but it is not allowed to store any customer or business related information on them. Flash drives provided by Smoking Games are allowed to use inside the companies network, but not in the wireless area or outside of the building. The same applies for other mobile devices provided by Smoking Games.\\
All employees are required to properly secure their work equipment as a part of the employee contract they have signed with the company. In return the company promises to give adequate education on how to secure their equipment. This kind of security measures includes anti-virus,
secure communication, physical security, clear-desk policy and other relevant topics. These rules are set by the Blueberry ITs security policy and guidelines.\\
Smoking Games have an incremental daily backup strategy and a complete back-up each Friday night. These back-ups are stored both on site and off site. The off site storage facility is a third party service provider, which complies with the same policies and legislative demands as Smoking Games.\\