\section{Business Unit Analysis}\label{sec:BusinessUnitAnalysis}
In this section the different units and processes will be analyzed and prioritized so we can stablish an order for the recovery in case of a successful attack. For this purpose table 2-3 \cite{whitman3} is used as a template. For the prioritization in the following, weights and categories will be used. The impact on profitability, being the most important counts 40\% of the final weight. Contribution to strategic objectives being the second most important will be 30\% of the final weight. On the third position, due to the importance on the public image of the enterprise, is the impact on the public image (weighted 20\%). Last but not least, impact on internal operations is the last 10\% of the final weight.

\begin{longtable}{| p{2.7cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} | p{.8cm} |}
		\caption{Weighted Business Unit Analysis}\label{tab:BUA}\\
		%the following until endfirsthead goes on top of table on first page
		\hline \multicolumn{6}{|p{12.4cm}|}{\textbf{Weighted Business Unit Analysis}}\\\hline
		\textbf{Business Functions} & \textbf{Impact on Probability} & \textbf{Contribution to Strategic Objectives} & \textbf{Impact on Public Image} & 	\textbf{Impact on Internal Operations} & \textbf{Total}\\
		  & \textbf{0.4} & \textbf{0.3} & \textbf{0.2} & \textbf{0.1} & \textbf{1}\\\hline
		\endfirsthead
		%the following until endhead goes on top of table of every page except first page
		\textbf{Business Functions} & \textbf{Impact on Probability} & \textbf{Contribution to Strategic Objectives} & \textbf{Impact on Public Image} & 	\textbf{Impact on Internal Operations} & \textbf{Total}\\
		 & \textbf{0.4} & \textbf{0.3} & \textbf{0.2} & \textbf{0.1} & \textbf{1}\\\hline
		\endhead
		%the following until endfoot goes at bottom of table except last page
		\multicolumn{5}{|c|}{\textit{continued on next page}}\\
		\endfoot
		%the following until endlastfoot goes at bottom of table on last page
		\endlastfoot
		Create New Games & 0.8 & 1 & 1 & 0 & 0.82\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{Inability to continue the creation of new games. This will result in a big loss, delays in the hand in of the game, and unsatisfied customers. The internal operations in the other hand will not be very affected.}}\\\hline
		Sign New Games Contracts & 0.8 & 0.7 & 0.9 & 0.1 & 0.72\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{This will make impossible to update the catalogue of games, affecting the public image and the revenue. In the other hand, the internal operations will not be affected.}}\\\hline
		Game sales & 0.9 & 0.4 & 0.9 & 0.4 & 0.7\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{Being the most important source of revenue is one of the most important parts of the business. Because it's not the most important in the philosophy of the enterprise it doesn't have the first position.}}\\\hline
		Provide Internet Services & 0.8 & 0.4 & 0.9 & 0.8 & 0.7\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{This is the second most important operation from the point of view of a customer. Without being able to download, save or share their games, the customer revenue will go down. It also causes problems for the marketing and selling of games.}}\\\hline
		Enroll new customers & 0.9 & 0.6 & 0.4 & 0.1 & 0.63\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{The enrollment of new customers is the first step towards them buying games. It doesn't have a high value in internal operation because old customers can still make a good revenue.}}\\\hline
		Advertise Services & 0.6 & 0.4 & 0.6 & 0 & 0.48\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{The main source of advertisement in the enterprise is carried inside the web services. This means that when the web services are up again the restoring of the advertisement will be easier. Even though is still important to keep it up as much as possible.}}\\\hline
		Customer support & 0.3 & 0.3 & 0.8 & 0 & 0.37\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{In this case the impact in the profit is really low, but it still being in the list. This is possible because of the great impact over the public image of the enterprise.}}\\\hline
		HR Processes & 0 & 0.5 & 0 & 0.6 & 0.21\\\hline
		& \multicolumn{5}{|p{9cm}|}{\textit{The HR operations are the less important in any aspect, the recovery will take place once everything else is on the way to work perfectly.}}\\\hline
\end{longtable}