\section{Identification of Threats and Attacks}\label{sec:IdentThreatsAttacks}
In this section the list of threats discovered in the risk identification process\ref{RiskIdent} is being converted into a prioritized list of attacks. For this a Weighted Business Risk Analysis (WBRA) is being performed: the threats are weighted with a 50-50 split between probability and consequence, though consequence is divided into damage cost (30\%) and repair cost (20\%). Each threat scenario is followed by a short discription, which gives an explanation about the weights that are given. It is arranged by the "Total" value (from high to low). Prioritization of each scenario is based upon which resources are most valuable to the company. Preservation of human lifes is always prioritized.\\
Table \ref{ref:tabWBRA} shows the results of the WBRA and is derived from table 2-2 \cite{whitman2}.\\
\begin{longtable}{| p{4.2cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} |}
		\caption{Weighted Business Risk Analysis}\label{ref:tabWBRA}\\
		%the following until endfirsthead goes on top of table on first page
		\hline \multicolumn{5}{|c|}{\textbf{Weighted Business Risk Analysis}}\\\hline
		\textbf{Threat} & \textbf{Probability (0.5)} & \textbf{Damage Cost (0.2)} & \textbf{Repair Cost (0.3)} & \textbf{Total (1.0)}\\\hline
		\endfirsthead
		%the following until endhead goes on top of table of every page except first page
		\textbf{Threat} & \textbf{Probability (0.5)} & \textbf{Damage Cost (0.2)} & \textbf{Repair Cost (0.3)} & \textbf{Total (1.0)}\\\hline
		\endhead
		%the following until endfoot goes at bottom of table except last page
		\multicolumn{5}{|c|}{\textit{continued on next page}}\\
		\endfoot
		%the following until endlastfoot goes at bottom of table on last page
		\endlastfoot
		Fire & 0.5 & 0.9 & 0.8 & 0.67\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The likelihood for a fire to occur is moderate because of the mostly warm weather; the damage cost is very high; the repair cost is high, because equipment or building parts need to be repaired.}}\\\hline
		Denial of service attack & 0.7 & 0.8 & 0.5 & 0.66\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Very likely to happen; would cause high damage, because customers/users won't have access to the servers.}}\\\hline
		Social engineering attack via e-mail & 0.8 & 0.6 & 0.4 & 0.64\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Very likely that some phishing e-mails will go through the spam-filter, but it would most likely cause minimal damage because of routines.}}\\\hline
		Information leakage & 0.5 & 0.8 & 0.8 & 0.63\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{High damage and high risk. It also has a high cost because it is difficult to discover and most likely not fixable.}}\\\hline
		Strong winds & 0.7 & 0.5 & 0.6 & 0.63\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Likely to occur; the damage cost is moderate due to the fact Smoking Games does not have any assets exposed other than it may be temporary loss of third party services; the repair cost is also moderate since building damage needs to be repaired.}}\\\hline
		Vulcanic eruption & 0.5 & 0.6 & 0.8 & 0.61\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Vulcanic eruptions are very likely to happen due to the location; damage cost varies by severity; repair costs are high because systems/building need to be repaired/restored.}}\\\hline
		Loss of user equipmment & 0.6 & 0.3 & 0.7 & 0.57\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This is not uncommon since users might break or loose their equipment; the damage cost is moderate since it's only the equipment which is lost; the repair cost is also moderate to high since the euipment needs to be replaced.}}\\\hline
		Social engineering attack via phone & 0.5 & 0.6 & 0.6 & 0.55\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Likely to happen because the phone numbers are accessible through the website; the damage however would likely be small because of procedures against exactly this kind of incidents.}}\\\hline
		Destruction of project management system & 0.2 & 0.8 & 0.9 & 0.53\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The likelihood of someone destroying the project management system is low, though in the case of such an incident the damage cost is high; the repair cost is extreme due to the fact that it's necessary to repair, replace and restore the systems.}}\\\hline
		Unauthorized software installation & 0.6 & 0.5 & 0.4 & 0.52\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The probability for this act is low, but it will probably take time and resources to repair.}}\\\hline
		Destruction of finance system & 0.2 & 0.8 & 0.8 & 0.5\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Destruction of the finance system is very unlikely to happen; the damage is high due to loss of customer accounts and billing information; the cost of repairing this system is also significantly high due to the restoration and improving of the system.}}\\\hline
		Internet outage & 0.4 & 0.9 & 0.4 & 0.5\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Rather unlikely to happen; damage cost is very high, because customers/users can't access the servers;  repair cost is rather low, because in most cases the ISP needs to make sure Smoking Games is conencted to the Internet.}}\\\hline
		Loss of information & 0.5 & 0.4 & 0.5 & 0.48\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This is not uncommon since information is often transported by portable storage mediums; the damage cost is moderate since storage mediums are encrypted; repair cost is moderate since Smoking Games must initiate an investigation and then implement proper counter measures.}}\\\hline
		Lightning & 0.3 & 0.7 & 0.6 & 0.47\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The chances for this incident to occur is low due to in-place countermeasures; the damage cost is high because all the IT-system is connected to the infrastructure; repair cost is also high since the systems need to be repaired or restored.}}\\\hline
		Worm in the internal network & 0.3 & 0.7 & 0.6 & 0.47\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{With strict access routines and well educated staff, the likelihood is small; the damage however could be very severe; it would take a moderate amount of time and resources to fix the network.}}\\\hline
		Water leakage & 0.3 & 0.7 & 0.6 & 0.47\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This happens rarely but can be costly and inconvenient when it does happen; both in external costs and resources wasted handling the incident.}}\\\hline
		Flood & 0.2 & 0.7 & 0.7 & 0.45\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The chance for a flood to occur is low; the damage cost to business for inability to properly function is moderate to high, as well es the repair costs.}}\\\hline
		Destruction of the buildings structure & 0.4 & 0.5 & 0.5 & 0.45\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This is a probable attack which may occur; the cost of the damage is moderate since it will result in lost work time and business functionality; the repair cost is also moderate due to the fact it results in higher rent, along with a split repair cost.}}\\\hline
		Unauthorized access to wireless network & 0.5 & 0.4 & 0.4 & 0.45\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{A basic WPA2 encrypted network is unlikely to crack, but the network is very little used and would probably be detected early.}}\\\hline
		Unauthorized access to work laptop & 0.4 & 0.6 & 0.4 & 0.44\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{All laptops are encrypted so the most likely attack vector is via malware; it does contain sensitive information and could be used to further attacks so the damage could be large.}}\\\hline
		Accidental deletion of data & 0.7 & 0.3 & 0.1 & 0.44\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Very likely to happen; usually this will not make a big difference to the organization mainly because of backups and subversion systems.}}\\\hline
		Theft of finances & 0.3 & 0.8 & 0.4 & 0.43\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This incident happens rarely, but may happen either by error or deliberately; the damage cost is high since it will result in loss of finances and possibly in large faults in the accounting and loss of employees; the repair cost is moderate since it will result in a complete revision of the accounting and lawsuits.}}\\\hline
		Destruction of access control system & 0.3 & 0.5 & 0.6 & 0.43\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The destruction of the access control system is not likely, but probable due to the fact of its exposed placements; the damage cost is moderate; the repair cost is somewhat higher due to the process of restoring and enhancing the system.}}\\\hline
		Sabotage of access control equipment & 0.5 & 0.4 & 0.3 & 0.42\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Sabotaging the access control system is likely to happen, since there are several people allowed to access it; the damage cost is moderate; the repair cost is low since it is an external service.}}\\\hline
		Sabotage of project and finance system & 0.3 & 0.3 & 0.7 & 0.42\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The chances of sabotaging either system is not very likely; the damage cost is low since the systems are properly secured and monitored; the repair cost is high due to the work needed to restore and improve the security, along with pursuing the incident.}}\\\hline
		Hard-disk on backup server crashes & 0.4 & 0.3 & 0.5 & 0.41\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The backup procedures are redundant which makes sure that there is more than one copy; most losses are based on time and resources spent; however, it is quiet likely to happen.}}\\\hline
		Unauthorized access to file server & 0.3 & 0.7 & 0.4 & 0.41\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The file server is placed securely on the internal network and to access it unauthorized is very difficult; it does contain sensitive information that could be severe if it falls into the wrong hands; backups make it easy to restore.}}\\\hline
		Functional bugs in 3rd party software & 0.6 & 0.2 & 0.2 & 0.40\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{These kinds of bugs might have a slight impact on the business, but it will most likely be corrected fast and it will be barely noticeable.}}\\\hline
		Unauthorized access to database & 0.3 & 0.8 & 0.3 & 0.40\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The database is well secured on the internal network;  compromise could cause severe damage to reputation, but backups would help to restore it relatively easy.}}\\\hline
		Sabotage of physical documents & 0.4 & 0.7 & 0.3 & 0.38\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The chances of sabotaging physical documents is moderate since they are stored in a secured file cabinet; the damage cost is low; the repair cost is moderate since a complete check of the inventory has to be done.}}\\\hline
		Unauthorized access to VPN account & 0.3 & 0.4 & 0.5 & 0.38\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The biggest attack vector here is weak passwords for which there are strict routines against it; this is an intermediate attack which an attacker could use to further compromise assets.}}\\\hline	
		Web site defacement & 0.6 & 0.5 & 0.5 & 0.37\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Likely to happen; causes severe damage to reputation; the cost to repair would be moderate.}}\\\hline
		Accidental removal of critical equipment & 0.3 & 0.5 & 0.4 & 0.37\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The probability that this error will occur is low, but mistakes do happen; the impact of this will be moderate because critical equipment or information storage devices will be unaccounted for, but only temporary lost and not stolen.}}\\\hline
		Unauthorized physical access to restricted areas & 0.2 & 0.6 & 0.5 & 0.37\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{These areas have enhanced security, which in return makes the cost of repairing and replacing the access control system higher.}}\\\hline
		Theft of information & 0.3 & 0.2 & 0.6 & 0.37\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Occurs rarely, but is not uncommon either; even though the damage cost is low since the information is encrypted and physical information is not to be of a sensitive nature; repair cost is moderate since Smoking Games must initiate an investigation and then implement proper counter measures.}}\\\hline
		Destruction of emergency systems & 0.3 & 0.5 & 0.4 & 0.37\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This is not likely, but still possible due to its natural placement and implementation; the damage cost is moderate, since it needs to be maintained; the repair cost is moderate, since it requires additional testing and repair work before its functional again.}}\\\hline
		Earthquake & 0.4 & 0.5 & 0.7 & 0.36\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Earthquakes are likle to occur because of the location; damage cost varies by severity of the earthquake; repair costs are high because it is necessary to replace and restore the systems/building.}}\\\hline
		Filing error & 0.5 & 0.1 & 0.3 & 0.36\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Happens from time to time, but no information is lost.}}\\\hline
		Hard-disk on laptop crashes & 0.4 & 0.3 & 0.3 & 0.35\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{All employees are required to do backups regularly so most costs are replacing and configuring the new work environment.}}\\\hline
		Hard-disk on file server crashes & 0.4 & 0.3 & 0.3 & 0.35\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This would cause problems with the daily operation very fast, but good backup routines ensure that very little or no data will be lost.}}\\\hline
		Hard-disk on database server crashes & 0.4 & 0.3 & 0.3 & 0.35\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Good backup routines will make sure, that very little or no data is lost, but it still takes time recovering and cost to replace.}}\\\hline
		Hard-disk on web server crashes & 0.4 & 0.3 & 0.3 & 0.35\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{A backup server is in place so there will be very little downtime; most costs are directed towards setting the environment to the previous standards.}}\\\hline
		Vendor stops supporting software & 0.2 & 0.5 & 0.5 & 0.35\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Vendors  rarely stop security updates to a product suddenly, if they do it might take considerable resources to update the systems.}}\\\hline
		Loss of access credentials & 0.6 & 0.1 & 0.4 & 0.35\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Loss of access credentials is not uncommon; the damage is not significant since employees is trained to report loss; the repair cost is moderate, since it is only a matter of disabling and issuing a new ID and PIN.}}\\\hline
		Unauthorized physical access to the premises & 0.3 & 0.4 & 0.4 & 0.35\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{A proper physical security is implemented, the damage is covered by other threats; the damage cost and repair cost is for covering repair and replacement of the access control system.}}\\\hline
		Unauthorized physical access to Smoking Games's internal facilities & 0.1 & 0.6 & 0.5 & 0.32\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{The areas within Smoking Games's office is also secured with enhanced security and the damage cost is covered by other threats.}}\\\hline
		Theft of access credentials & 0.3 & 0.3 & 0.3 & 0.30\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Happens rarely; the damage is not severe since employees are trained to report this type of incident; the repair cost is low since it only involves disabling and issuing a new ID-card with a new PIN.}}\\\hline
		Theft of user equipment & 0.2 & 0.3 & 0.4 & 0.28\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{Happens rarely; the damage cost is moderate since it contains information and access to the business secured network, though the entire system is encrypted and will wipe itself in case of theft; the repair cost is moderate since it's necessary to replace the equipment and implement mitigating controls for the incident.}}\\\hline
		Power outage & 0.4 & 0.2 & 0.1 & 0.27\\\hline
		& \multicolumn{4}{|p{8cm}|}{\textit{This happens rarely and is usually very short when it does happen; a backup-power-generator will operate in case of emergency.}}\\\hline
\end{longtable}


%information leakage
%social engineering attack via email
%destruction of project management system
%flood, lightning, fire, earthquake, tsunami
%unauthorized software installation
%loss of information
%worm in the internal network
%water leakage
%destruction of the buildings structure
%unauthorized access to wireless network
%destruction of finance system
%loss of user equipmment
%unauthorized access to work laptop
%accidental deletion of data
%sabotage of access control eqipment
%sabotage of project and finance system
%hard disk on backup server crashes
%unauthorized access to file server
%functional bugs in 3rd party software
%theft of finances
%sabotage of physical documents
%unauthorized access to database
%unauthorized access to VPN account
%web site defacement
%accidental removal of critical equipment
%unauthorized physical access to restricted areas
%unauthorized physical access to Smoking Games's internal facilities
%filing error
%social engineering attack via phone
%hard disk on laptop crashes
%hard disk on file server crashes
%hard disk on database server crashes
%hard disk on web server crashes
%vendor stops supporting software
%loss of access redentials
%unauthorized physical access to the premises
%theft of information
%decial of service against assets
%destruction of access control system
%destruction of emergency systems
%theft of user equipment
%power outage
%theft of access credentials
%string winds
%internet outage
%power burnout


%\subsection{Business Processes and Recovery Criticality}
%Smoking Games's can roughly be divided into 4 business areas: financial system, business intelligence (e.g. project managers), sales and marketing, and game/software development. In order to keep the company in business, it is crucial to determine the business processes of each business area and evaluate them based on costs of failure. This includes the outage of a process, the delay, and the longest time a process could be left without being performed.
%\begin{table}[h]
%	\centering
%	\begin{tabular}{| l | c | c | c | c | c |}
%		\hline
%		\textbf{\parbox[t]{2cm}{Business\\Function}} & \textbf{\parbox[t]{2cm}{Impact on\\Profitability\\(40\%)}} & \textbf{\parbox[t]{2cm}{Contribution to\\Strategic\\Objectives\\(30\%)}} & \textbf{\parbox[t]{2cm}{Impact on\\Internal\\Operations\\(20\%)}} & \textbf{\parbox[t]{2cm}{Impact on\\Public Image\\(10\%)}} & \textbf{\parbox[t]{2cm}{Total\\Weights\\(100\%)}}\\\hline
%		Providing Internet services
%		
%	\end{tabular}
%	\caption{Weighted Business Risk Analysis}\label{ref:tabWBRA}
%\end{table}


