\section{Subordinate Plan Classification}\label{sec:SubordPlanClass}
The last part of the BIA is the Subordinate Plan Classification which dictates what plans is to be made for the corresponding attack scenario and who it is passed on to. This template used is taken from the book ”Principles of Incident Response and Disaster Recovery”\cite{whitman6}.\\
\begin{longtable}{| p{4cm} | p{8cm} |}
	\hline \multicolumn{2}{| c |}{\textbf{Denial of Service Attack: Addendum}}\\\hline
	\endfirsthead
	
	\hline \multicolumn{2}{| c |}{\textbf{Denial of Service Attack: Addendum} ...continued}\\\hline
	\endhead
	
	\multicolumn{2}{|r|}{\textit{continued on next page}}\\\hline
	\endfoot
	
	\endlastfoot
	
	Date of analysis: & 12.01.2014 \\\hline
	
	Attack name/description: &  Denial of service attack against the web services of Smoking Games.\\\hline
	
	Threat agents: & Competitors, Hackers, Organized crime.\\\hline
	
	\multicolumn{2}{| c |}{\textbf{Subordinate plan classification}}\\\hline
	\multicolumn{2}{| p{12cm} |}{
		\paragraph{Description:} This attack is passed on to the incident response planning team for developing incident response plans for the attack. After the incident response plans are finished, they, along with this document shall be passed on to the disaster recovery planning team. They will then develop disaster recovery plans in case of an escalation of the initial incident. This incident will require a business continuity plan to be developed. This plan must dictate how to temporarily replace and restore the original IT-systems when a disaster has occurred. At both levels the mitigating actions should be specified along with current policies and guidelines for properly removing software and contaminated systems. In addition guidelines should be specified for properly upholding sanctions for a breach of policy.}\\\hline
\end{longtable}

\begin{longtable}{| p{4cm} | p{8cm} |}
	\hline \multicolumn{2}{| c |}{\textbf{Fire: Addendum}}\\\hline
	\endfirsthead
	
	\hline \multicolumn{2}{| c |}{\textbf{Fire: Addendum} ...continued}\\\hline
	\endhead
	
	\multicolumn{2}{|r|}{\textit{continued on next page}}\\\hline
	\endfoot
	
	\endlastfoot
	
	Date of analysis: & 07.02.2014 \\\hline
	
	Attack name/description: &  Fire in the Smoking Games headquarters.\\\hline
	
	Threat agents: & blown cables, computers etc., arson\\\hline
	\multicolumn{2}{| c |}{\textbf{Subordinate plan classification}}\\\hline
	\multicolumn{2}{| p{12cm} |}{
		\paragraph{Description:} This attack is passed on to the incident response planning team for developing incident response plans for the attack. After the incident response plans are finished, they, along with this document shall be passed on to the disaster recovery planning team. They will then develop disaster recovery plans in case of an escalation of the initial incident. This plan also requires a business continuity plan for relocating to a temporary location and back to a permanent location. Nonetheless, the fire department should be called.}\\\hline
\end{longtable}